\customsection
    {Further Experience}
    {\myindent In my free time I like to challenge myself and work on fun projects that are featured on my blog \myurl{https://budavariam.github.io}{here}.
    To help others I developed two different hybrid mobile applications with Ionic for medical research,
    and created a controller dashboard for a PLC driven smart home system.
    I love participating in \myurl{https://budavariam.github.io/tags/hackathon/}{hackathons}.
    In addition to these, I like to solve coding challenges in
    \myurl{https://app.codesignal.com/profile/budavariam}{codesignal.com},
    \myurl{https://github.com/budavariam/advent_of_code}{adventofcode.com},
    \myurl{https://cssbattle.dev/player/budavariam}{cssbattle.dev},
    and \myurl{https://regexcrossword.com/}{regexcrossword.com}.
    \\
    \vspace{-\baselineskip}
        \begin{multicols}{2}
        \begin{itemize}
            \item Charts in Plotly.js / Dash
            \item 3D modeling in Three.js
            \item IoT with Raspberry Pi / ESP32
            \item Web Components for my static sites
        \end{itemize}
        \end{multicols}


    \myindent In 2020 I taught a \textbf{Linux fundamentals} course at Starschema.
    I created the course materials by myself and I learned a lot from this teaching experience.
    I'd like to keep sharing my knowledge with others.
    In 2024 I had a chance to teach again, this time \textbf{Debugging methods} with Python.}
%
\customsection{Languages}
    {\textbf{English} - \textit{TELC B2 Complex language exam} - \textit{2014} \\
    \myindent\small{Active, fluent, technical, written and spoken knowledge.}}
%
\customsection{Driving license}
    {\textbf{B Category} - \textit{Szeged, Hungary}}
%
\customsection{Hobbies}
    {I enjoy living a \textbf{healthy} lifestyle, I take \textbf{kettlebell} classes.
    \textbf{Music} is important to me, I studied classical \textbf{guitar} for 10 years.
    I sang as a tenor in \textbf{Keep Smiling Jazz Vocal} choir.
    I love board games, and I'm a huge fan of \textbf{permutational puzzles}.
    I'm into calligraphy and watercolor painting.}