\cvsection{Work Experience}

\workentry
    {ex-Starschema}
    {Budapest}
    {Senior Software Developer Team Lead}
    {Currently working here since \textbf{Jan. 2019}}
    {}
    {I work as a \textbf{full-stack web developer}. I love \textbf{DevOps} related tasks and working with \textbf{databases}
    and setting up connections or integrations to third party services.
    Besides my development tasks, I always aim to improve the \textbf{developer experience} on my projects.
    As a senior developer I participate in \textbf{architectural design} and \textbf{planning} for incoming projects.
    I'm also a \textbf{team lead} of five developers. I'm there when they need any support.
    I follow how they're doing and help them \textbf{grow}.}
    {\vspace{-\baselineskip}
    \begin{multicols}{3}
    \begin{itemize}
        \item React.js
        \item Go
        \item Kubernetes
        \item Python
        \item TypeScript
        \item AWS
    \end{itemize}
    \end{multicols}}
%
\workentry
    {MioLabs}
    {Alicante}
    {Full-stack developer}
    {12 months from \textbf{Jan. 2018} to \textbf{Dec. 2018}}
    {}
    {%
    At MIO Research Labs we developed a web framework in \textbf{TypeScript}, and used it for our projects. My tasks were related to discovering, evaluating, and implementing solutions with newer technologies to maximize efficiency. I \textbf{improved workflows} and \textbf{created tools} for the framework. I also participated in the development and the deployment of our web applications, \textbf{backend services} and websocket servers that ran in AWS.
    }
    {\vspace{-\baselineskip}
    \begin{multicols}{3}
    \begin{itemize}
        \item \small{Typescript}
        \item \small{Node.js}
        \item \small{Webpack}
        \item \small{AWS EB}
        \item \small{Python}
        \item \small{Docker}
    \end{itemize}
    \end{multicols}}
%
\workentry
    {Océ}
    {Szeged}
    {Frontend developer}
    {8 months from \textbf{Feb. 2017} to \textbf{Oct. 2017}}
    {}
    {At OSRH I took part in the continuous development of \textbf{Irista}, the former photo and video sharing service of \textbf{Canon}. Later I worked on the website of the \textbf{Print Rewards} program.}
    {\vspace{-\baselineskip}
    \begin{multicols}{3}
    \begin{itemize}
        \item \small{Angular.js\\(Javascript, HTML5, SCSS, Grunt)}
        \item \small{Angular 2/4\\(Typescript, ES6, rxjs, webpack)}
        \item \small{MongoDb}
    \end{itemize}
    \end{multicols}}
%
\workentry
    {Mongúz kft.}
    {Szeged}
    {Full-stack developer}
    {37 months from \textbf{Jan. 2014} to \textbf{Feb. 2017}}
    {}
    {The company's main profile is to develop software for libraries, museums and attractions. We were dealing with a huge amount of data spanning from full-text search from books to importing and exporting bibliographical data. I was working on \textbf{new features} in several of our projects. I implemented \textbf{backend services} and \textbf{UI} parts together.}
    {\vspace{-\baselineskip}
    \begin{multicols}{2}
    \begin{itemize}
        \item \small{Angular.js\\(Javascript, HTML5, SCSS, Gulp)}
        \item \small{Java (Spring, Maven, Hibernate ORM)}
        \item \small{PostgreSQL}
    \end{itemize}
    \end{multicols}}